The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents

### 2024-02-13 main_folder/paper/paper.qmd
changed main file name

####Make Figure 1####
# Only show the top 10 rows of our table since there's more than 2000 rows in total
# Scatter plot
ggplot(raw_data_full, aes(x = aggression, y = hostile_offline)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue", linetype = "dashed") +
  labs(x = "Agression", y = "Hostile Offline Score") 
```

@@

####Make Figure 1####
# Only show the top 10 rows of our table since there's more than 2000 rows in total
# Scatter plot
ggplot(raw_data_full, aes(x = aggression, y = hostile_online)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue", linetype = "dashed") +
  labs(x = "Agression", y = "Hostile Online Score") 
```

@@

####Make Figure 3####
# Make a Scatter plot
ggplot(raw_data_full, aes(x = aggression, y = online_offline)) +
  geom_point(color = "skyblue", size = 3, alpha = 0.7) +  # Customize point appearance
  geom_smooth(method = "lm", se = FALSE, color = "darkblue", linetype = "dashed") +  # Add best-fit line
  labs(x = "Aggression", y = "Difference of Hostile Online and Offline") +
  theme_minimal() +  # Use a minimal theme for a professional look
  theme(
    axis.text = element_text(size = 12, color = "black"),  # Customize axis text size and color
    axis.title = element_text(size = 12, color = "black", face = "bold"),  # Customize axis title size, color, and style
    plot.title = element_text(size = 12, color = "black", face = "bold"),  # Customize plot title size, color, and style
    panel.background = element_rect(fill = "white", color = "black"),  # Customize panel background color
    panel.grid.major = element_line(color = "lightgray"),  # Customize major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    legend.position = "none"  # Remove legend
  ) 
```

@@

####Calculate the t-test result between Online and Offline hostile score
t_test_onoff_total <- t.test(raw_data_full$hostile_online, raw_data_full$hostile_offline)

t_test_onoff_us <- t.test(raw_data_us$hostile_online, raw_data_us$hostile_offline)

t_test_onoff_dk <- t.test(raw_data_dk$hostile_online, raw_data_dk$hostile_offline)

t_test_on_dkus <- t.test(raw_data_us$hostile_online, raw_data_dk$hostile_online)

t_test_off_dkus <- t.test(raw_data_us$hostile_offline, raw_data_dk$hostile_offline)

pvalue <- c(t_test_onoff_total$p.value, t_test_onoff_us$p.value, t_test_onoff_dk$p.value, t_test_on_dkus$p.value, t_test_off_dkus$p.value)
tvalue <- c(t_test_onoff_total$statistic, t_test_onoff_us$statistic, t_test_onoff_dk$statistic, t_test_on_dkus$statistic, t_test_off_dkus$statistic)
df <- c(t_test_onoff_total$parameter, t_test_onoff_us$parameter, t_test_onoff_dk$parameter, t_test_on_dkus$parameter, t_test_off_dkus$parameter)

t_test_table <- tibble(
  Nation = c("Total on_off", "US on_off", "DK on_off", "USDK on", "USDK off"),
  P_Value = pvalue,
  T_Value = tvalue,
  DF = df
)

t_test_table$P_Value <- format(t_test_table$P_Value, scientific = TRUE)
t_test_table$T_Value <- format(round(t_test_table$T_Value, 4), nsmall = 4,scientific = FALSE)

kable(t_test_table)
```

@@

us_mean_on <- mean(raw_data_us$hostile_online)
us_mean_off <- mean(raw_data_us$hostile_offline)
dk_mean_on <- mean(raw_data_dk$hostile_online)
dk_mean_off <- mean(raw_data_dk$hostile_offline)

mean_table <- tibble(
  Category = c("US_ON", "US_OFF", "DK_ON", "DK_OFF"),
  Mean = c(us_mean_on, us_mean_off, dk_mean_on, dk_mean_off)
)

kable(mean_table)
```

>>>>

####Make Figure 1####
# Scatter plot with a best fit line
ggplot(raw_data_full, aes(x = aggression, y = hostile_offline)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue", linetype = "dashed") +
  labs(x = "Agression", y = "Hostile Offline Score") 
```

@@

####Make Figure 2####
# Scatter plot with a best fit line
ggplot(raw_data_full, aes(x = aggression, y = hostile_online)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue", linetype = "dashed") +
  labs(x = "Agression", y = "Hostile Online Score") 
```

@@

####Make Figure 3####
# Make a Scatter plot
ggplot(raw_data_full, aes(x = aggression, y = online_offline)) +
  geom_point(color = "skyblue", size = 3, alpha = 0.7) +  # Customize point appearance
  geom_smooth(method = "lm", se = FALSE, color = "darkblue", linetype = "dashed") +  # Add a  best-fit line
  labs(x = "Aggression", y = "Difference of Hostile Online and Offline") +
  theme_minimal() +  # Use a minimal theme for a better look
  theme(
    axis.text = element_text(size = 12, color = "black"),  # Customize axis text
    axis.title = element_text(size = 12, color = "black", face = "bold"),  # Customize axis title
    plot.title = element_text(size = 12, color = "black", face = "bold"),  # Customize plot title
    panel.background = element_rect(fill = "white", color = "black"),  # Customize panel background
    panel.grid.major = element_line(color = "lightgray"),  # Customize major grid lines
    panel.grid.minor = element_blank(),  # Remove minor grid lines
    legend.position = "none"  # Remove legend
  ) 
```

@@

####Calculate the t-test result between Online and Offline hostile score####
#The t-test result between Total Online and Offline hostile score
t_test_onoff_total <- t.test(raw_data_full$hostile_online, raw_data_full$hostile_offline)
#The t-test result between US Online and Offline hostile score
t_test_onoff_us <- t.test(raw_data_us$hostile_online, raw_data_us$hostile_offline)
#The t-test result between DK Online and Offline hostile score
t_test_onoff_dk <- t.test(raw_data_dk$hostile_online, raw_data_dk$hostile_offline)
#The t-test result between US and DK Online hostile score
t_test_on_dkus <- t.test(raw_data_us$hostile_online, raw_data_dk$hostile_online)
#The t-test result between US and DK Offline hostile score
t_test_off_dkus <- t.test(raw_data_us$hostile_offline, raw_data_dk$hostile_offline)
#add all of these t-test results to a tibble, only remain p value, t value and df
pvalue <- c(t_test_onoff_total$p.value, t_test_onoff_us$p.value, t_test_onoff_dk$p.value, t_test_on_dkus$p.value, t_test_off_dkus$p.value)
tvalue <- c(t_test_onoff_total$statistic, t_test_onoff_us$statistic, t_test_onoff_dk$statistic, t_test_on_dkus$statistic, t_test_off_dkus$statistic)
df <- c(t_test_onoff_total$parameter, t_test_onoff_us$parameter, t_test_onoff_dk$parameter, t_test_on_dkus$parameter, t_test_off_dkus$parameter)

t_test_table <- tibble(
  Nation = c("Total on_off", "US on_off", "DK on_off", "USDK on", "USDK off"),
  P_Value = pvalue,
  T_Value = tvalue,
  DF = df
)
#format the numbers for better look
t_test_table$P_Value <- format(t_test_table$P_Value, scientific = TRUE)
t_test_table$T_Value <- format(round(t_test_table$T_Value, 4), nsmall = 4,scientific = FALSE)
#make a table
kable(t_test_table)
```

@@

#### Calculate the mean value for US and DK Online and Offline Hostile Score####
us_mean_on <- mean(raw_data_us$hostile_online)
us_mean_off <- mean(raw_data_us$hostile_offline)
dk_mean_on <- mean(raw_data_dk$hostile_online)
dk_mean_off <- mean(raw_data_dk$hostile_offline)
#add all of the values into a tibble
mean_table <- tibble(
  Category = c("US_ON", "US_OFF", "DK_ON", "DK_OFF"),
  Mean = c(us_mean_on, us_mean_off, dk_mean_on, dk_mean_off)
)
#make a table
kable(mean_table)
```
